Supplementary Appendix: Trends in the contribution of major causes of death

### 2018-05-10 Manuscript/Appendix-agestd-mort-rates.Rmd
update appendix

---
title: "Supplementary Appendix: Trends in the contribution of major causes of death to the black-white life expectancy gap by US state. A retrospective study of all deaths between 1969 and 2013"
output: html_document
---

This is the supplementary appendix for the paper, "Trends in the contribution of major causes of death to the black-white life expectancy gap by US state. A retrospective study of all deaths between 1969 and 2013."

Corinne A Riddell, PhD; Kathryn T Morrison, PhD; Jay S Kaufman, PhD; Sam Harper, PhD;

Address correspondence to: Corinne Riddell, PhD, Department of Epidemiology, Biostatistics & Occupational Health, McGill University, 1020 Pine Avenue West, Room 36B, Montreal, QC H3A 1A2, Canada. Email: <corinne.riddell@mail.mcgill.ca>

```{r load_libraries, echo=FALSE, warning=F, message=F}
library(dplyr)
library(purrr)
library(ggplot2)
library(stringr)
library(reshape2)
library(grid)
library(gridExtra)
library(plotly)
library(forcats)
source("../Code/life_expectancy_functions.R")

@@

age_cod_results_infants_AOC <- read.csv("../Results2/age_cod_results_infants_AOC_cubic.csv")
age_cod_results_infants_AOC$stabbrs <- state.abb[match(age_cod_results_infants_AOC$state, state.name)]
age_cod_results_infants_AOC$stabbrs[age_cod_results_infants_AOC$state == "Washington DC"] <- "DC"
age_cod_results_infants_AOC <- reorder.as.map2(age_cod_results_infants_AOC, "state", "stabbrs")

cod_decomp_results <- read.csv("../Results2/cod_decomp_results_cubic.csv")
cod_decomp_results$COD <- factor(cod_decomp_results$COD, levels(cod_decomp_results$COD)[c(3, 2, 4, 6, 5, 1)])
```

@@

```{r print-em, fig.width = 9, fig.height = 7, echo = F}
Cardiovascular.Male.mort.plot[[3]] %>% layout(margin = list(b = 100, l = 70))
#Cardiovascular.Male.mort.plot[[4]]
```

@@

```{r print-em-2, fig.width = 9, fig.height = 7, echo = F}
Cardiovascular.Female.mort.plot[[3]] %>% layout(margin = list(b = 100, l = 70))
#Cardiovascular.Female.mort.plot[[4]]
```

@@

```{r print-em-3, fig.width = 9, fig.height = 7, echo = F}
Cancers.Male.mort.plot[[3]] %>% layout(margin = list(b = 100, l = 70))
#Cancers.Male.mort.plot[[4]]
```

@@

```{r print-em-4, fig.width = 9, fig.height = 7, echo = F}
Cancers.Female.mort.plot[[3]] %>% layout(margin = list(b = 100, l = 70))
#Cancers.Female.mort.plot[[4]]
```

@@

```{r, fig.width = 9, fig.height = 7, echo = F}
`Non-communicable.Male.mort.plot`[[3]] %>% layout(margin = list(b = 100, l = 70))
#`Non-communicable.Male.mort.plot`[[4]]
```

@@

```{r, fig.width = 9, fig.height = 7, echo = F}
`Non-communicable.Female.mort.plot`[[3]] %>% layout(margin = list(b = 100, l = 70))
#`Non-communicable.Male.mort.plot`[[4]]
```

@@

```{r, fig.width = 9, fig.height = 7, echo = F}
Injuries.Male.mort.plot[[3]] %>% layout(margin = list(b = 100, l = 70))
#Injuries.Male.mort.plot[[4]]
```

@@

```{r, fig.width = 9, fig.height = 7, echo = F}
Injuries.Female.mort.plot[[3]] %>% layout(margin = list(b = 100, l = 70)) 
#Injuries.Female.mort.plot[[4]]
```

@@

```{r print-3, fig.width = 9, fig.height = 7, echo = F}
Communicable.Male.mort.plot[[3]] %>% layout(margin = list(b = 100, l = 70))
#Communicable.Male.mort.plot[[4]]
```

@@

```{r print-4, fig.width = 9, fig.height = 7, echo = F}
Communicable.Female.mort.plot[[3]] %>% layout(margin = list(b = 100, l = 70))
#Communicable.Female.mort.plot[[4]]
```

@@

```{r, fig.width = 9, fig.height = 7, echo = F}
`All other causes.Male.mort.plot`[[3]] %>% layout(margin = list(b = 100, l = 70))
#`All other causes.Male.mort.plot`[[4]]
```

@@

```{r, fig.width = 9, fig.height = 7, echo = F}
`All other causes.Female.mort.plot`[[3]] %>% layout(margin = list(b = 100, l = 70)) 
#`All other causes.Female.mort.plot`[[4]]
```

>>>>

---
title: 'Supplementary Appendix: Trends in the contribution of major causes of death
  to the black-white life expectancy gap by US state'
output:
  word_document: default
  html_document: default
---

This is the supplementary appendix for the paper, "Trends in the contribution of major causes of death to the black-white life expectancy gap by US state".

For an interactive version of all our results, please visit XXXX.

```{r load_libraries, echo=FALSE, warning=F, message=F}
#Corinne A Riddell, PhD; Kathryn T Morrison, PhD; Sam Harper, PhD; Jay S Kaufman, PhD

#Address correspondence to: Corinne Riddell, PhD, Department of Epidemiology, Biostatistics & Occupational Health, McGill University, #1020 Pine Avenue West, Room 36B, Montreal, QC H3A 1A2, Canada. Email: <corinne.riddell@mail.mcgill.ca>

library(dplyr)
library(purrr)
library(ggplot2)
library(stringr)
library(reshape2)
library(grid)
library(gridExtra)
library(plotly)
library(forcats)
source("../Code/life_expectancy_functions.R")

@@

age_cod_results_infants_AOC <- read.csv("../Results2/age_cod_results_infants_AOC_cubic.csv")
age_cod_results_infants_AOC$stabbrs <- state.abb[match(age_cod_results_infants_AOC$state, state.name)]
age_cod_results_infants_AOC$stabbrs[age_cod_results_infants_AOC$state == "Washington DC"] <- "DC"
age_cod_results_infants_AOC <- reorder.as.map2(age_cod_results_infants_AOC, "state", "stabbrs")
```

@@

```{r print-em, fig.width = 9, fig.height = 7, echo = F}
Cardiovascular.Male.mort.plot[[1]]
#Cardiovascular.Male.mort.plot[[3]] %>% layout(margin = list(b = 100, l = 70))
#Cardiovascular.Male.mort.plot[[4]]
```

@@

```{r print-em-2, fig.width = 9, fig.height = 7, echo = F}
Cardiovascular.Female.mort.plot[[1]]
#Cardiovascular.Female.mort.plot[[3]] %>% layout(margin = list(b = 100, l = 70))
#Cardiovascular.Female.mort.plot[[4]]
```

@@

```{r print-em-3, fig.width = 9, fig.height = 7, echo = F}
Cancers.Male.mort.plot[[1]]
#Cancers.Male.mort.plot[[3]] %>% layout(margin = list(b = 100, l = 70))
#Cancers.Male.mort.plot[[4]]
```

@@

```{r print-em-4, fig.width = 9, fig.height = 7, echo = F}
Cancers.Female.mort.plot[[1]]
#Cancers.Female.mort.plot[[3]] %>% layout(margin = list(b = 100, l = 70))
#Cancers.Female.mort.plot[[4]]
```

@@

```{r, fig.width = 9, fig.height = 7, echo = F}
`Non-communicable.Male.mort.plot`[[1]]
#`Non-communicable.Male.mort.plot`[[3]] %>% layout(margin = list(b = 100, l = 70))
#`Non-communicable.Male.mort.plot`[[4]]
```

@@

```{r, fig.width = 9, fig.height = 7, echo = F}
`Non-communicable.Female.mort.plot`[[1]]
#`Non-communicable.Female.mort.plot`[[3]] %>% layout(margin = list(b = 100, l = 70))
#`Non-communicable.Male.mort.plot`[[4]]
```

@@

```{r, fig.width = 9, fig.height = 7, echo = F}
Injuries.Male.mort.plot[[1]]
#Injuries.Male.mort.plot[[3]] %>% layout(margin = list(b = 100, l = 70))
#Injuries.Male.mort.plot[[4]]
```

@@

```{r, fig.width = 9, fig.height = 7, echo = F}
Injuries.Female.mort.plot[[1]]
#Injuries.Female.mort.plot[[3]] %>% layout(margin = list(b = 100, l = 70)) 
#Injuries.Female.mort.plot[[4]]
```

@@

```{r print-3, fig.width = 9, fig.height = 7, echo = F}
Communicable.Male.mort.plot[[1]]
#Communicable.Male.mort.plot[[3]] %>% layout(margin = list(b = 100, l = 70))
#Communicable.Male.mort.plot[[4]]
```

@@

```{r print-4, fig.width = 9, fig.height = 7, echo = F}
Communicable.Female.mort.plot[[1]]
#Communicable.Female.mort.plot[[3]] %>% layout(margin = list(b = 100, l = 70))
#Communicable.Female.mort.plot[[4]]
```

@@

```{r, fig.width = 9, fig.height = 7, echo = F}
`All other causes.Male.mort.plot`[[1]] 
#`All other causes.Male.mort.plot`[[3]] %>% layout(margin = list(b = 100, l = 70))
#`All other causes.Male.mort.plot`[[4]]
```

@@

```{r, fig.width = 9, fig.height = 7, echo = F}
`All other causes.Female.mort.plot`[[1]]
#`All other causes.Female.mort.plot`[[3]] %>% layout(margin = list(b = 100, l = 70)) 
#`All other causes.Female.mort.plot`[[4]]
```
